Why do we Eval?\\\Large A large-scale study of Eval usage in R

### 2021-03-15 paper/main.tex
Minimized expressions: % only one per site

The most common minimized expression is a variable. It happens in \packageMinimizedpropsitesa of the sites and is widespread across packages as it is found in \packageMinimizedpackagea packages across our CRAN corpus. The \c{envir} argument is explicitly passed in \packageMinimizedpercentenvira\% of the call sites, which suggests that \eval is used here to get the value of the variable in a non-local environment.

Note that a site can exhibit several minimized expressions. The most common combinations are:

@@

>>>>

The most common minimized expression is a variable.\footnote{An arithmetic with some variables and constant will also be normalized to \c{X}, i.e. a variable.} It happens in \packageMinimizedpropsitesa of the sites and is widespread across packages as it is found in \packageMinimizedpackagea packages across our CRAN corpus. The \c{envir} argument is explicitly passed in \packageMinimizedpercentenvira\% of the call sites, which suggests that \eval is used here to get the value of the variable in a non-local environment.

Compositions of functions, without variables, is the second most frequent minimized expression.

When a function is evaluated on some variable, the percentage of non default environment is high.

\c{FUN} represents a function definition

\c{{BLOCK}} is a sequence of statements. It is usually large, with in average \packageMinimizedoperationsjRnd operations in it.

The minimized expression classification suggests that the presence of variables in the expression is highly correlated to the specification of a specific environment, and that \eval is used here for its power in precising the evaluation environment.

Note that a site can exhibit several minimized expressions. However, \packageNbOneMinimizedPercent of the sites have only one minimized expression. The most common combinations are:

\NOTE{Maybe we should ditch the table of the minimized expressions and rather use the ones of combinations. It has the advantage of showing what is the most frequent, per call site. But it's a long tail, and sites that have several minimized expressions are not that numerous, only 13\%}

@@

\subsection{Logging}

\subsection{Code transform}

\subsection{Plotting}

\section{\eval expressivity and macros}

% The Thomas Lumley's article, Programmer's Niche: Macros in R, (https://www.r-project.org/doc/Rnews/Rnews_2001-3.pdf) describes how to write a `defmacro` function that would like as a macro creator, using `substitute` and `eval`.  There are no local macro variables in this implementation though.

\section{The dangers of \eval}
